Positivity-Preserving Adaptive Runge-Kutta Methods

### 2020-03-24 latex/overview.tex
Revise section 3.2.

% definitions
\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\CN}{\mathbb{C}}
\renewcommand{\H}{\mathcal{H}}
\renewcommand{\O}{\mathcal{O}}
\newcommand{\dt}{{\Delta t}}
\newcommand{\1}{\mathbbm{1}}
\newcommand{\e}{\mathrm{e}}
\newcommand{\scp}[2]{\left\langle{#1,\, #2}\right\rangle}
\newcommand{\I}{\operatorname{I}}
\newcommand{\lot}{\ell_{\mathrm{ot}}}
\newcommand{\ut}{\tilde{u}}
\newcommand{\bt}{\tilde{b}}

@@

\section{Adaptive RKM}\label{sec:LP}

In the following Section,  how the approach can be written as a LP. 
For this we have to consider which weights to choose. 
Generally, any $b \in \R^s$ can be used. 
One requirement would be that the new solution is positive.
We can further reduce this space by enforcing the order conditions. 
By incorporating the order conditions, the space of possible weights is limited to a subset of $\R^s$. %(Note: not linear because 0 is not in subspace)
Finally, we have to state an objective function to get the optimal weights.

@@

The order conditions for a RKM are a set of Equations depending on $A$, $c$ and $b$. In these Equations $b$ only appears linearly \cite{hairer_solving_1993}.
If $A$ and $c$ are already known, the order conditions for the order $p$ are a linear equations system and can be written as $Q b = r$.

The vector $b \in \R^s$ contains the weights and $Q$ is an $g \times s$ matrix, where $g$ is the number of order conditions. The vector $r$ contains the right hand side of the order conditions.

If the $A$ of a preexisting RK-method is used, there is at least one solution for the linear equation system.
In order to get an optimization problem, the equation system has to be underdetermined.
This implies that $\mathrm{rank}(Q) < s$. 
Because the quadrature conditions are linearly independent, there are at least $p$ independent vectors in $Q$. This leads to the condition $p < s$.
This implies that the number of stages has to be higher than the wanted order.

@@

\subsubsection{Adaption of Timestep using the dense output formual}

>>>>

% definitions
\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\CN}{\mathbb{C}}
\renewcommand{\H}{\mathcal{H}}
\renewcommand{\O}{\mathcal{O}}
\newcommand{\dt}{{\Delta t}}
\newcommand{\1}{\mathbbm{1}}
\newcommand{\e}{\mathrm{e}}
\newcommand{\scp}[2]{\left\langle{#1,\, #2}\right\rangle}
\newcommand{\I}{\operatorname{I}}
\newcommand{\lot}{\ell_{\mathrm{ot}}}
\newcommand{\ut}{\tilde{u}}
\newcommand{\bt}{\tilde{b}}
\newcommand{\pt}{{\tilde{p}}}

@@

\section{Selection of modified weights}\label{sec:LP}

In this Section, we consider the formulation of the LP to choose
the modified weights $\bt$.  In particular, we focus on the choice
of objective function and how to relax the constraints to ensure that
a feasible solution exists.

@@

The order conditions for an $s$-stage, order $p$ RKM are a set of equations depending on $A$, $b$ and
$c$.  As mentioned already, if $A$ and $c$ are given, the order conditions are
linear in $b$ and can be written as $Q_p b = r_p$, where
and $Q_p\in{\mathbb R}^{s\times s}, r_p\in{\mathbb R}^s$ represent the set of all conditions up to
and including order $p$.  It may not be possible to find modified weights
that also satisfy the conditions of order $p$ and yield positivity, so
in general the modified weights will be a solution of
$$
  Q_\pt \bt = r_\pt
$$
for some $\pt \le p$.   Since we have $s$ degrees of freedom $\bt_j$,  we need
at a minimum to choose $\pt$ so that $\mathrm{rank}(Q_\pt) < s$. 
Because the quadrature conditions are linearly independent, we have $\mathrm{rank}(Q_p)\ge p$,
so we must take $\pt \le s$.  In general we may need to take $\pt$ even smaller
in order to achieve positivity.

@@

\subsubsection{Adaption of Timestep using the dense output formula}
